Uncovering Ferry Traffic Patterns: A Data-Driven Study of Toronto Island Ticket Sales and Redemptions

### 2024-09-27 outputs/paper/paper.qmd
final draft upoaded

@fig-linePlot2 on the following page shows the Redemption and Sales Counts in months over years. The graph uses dashed lines to represent the monthly sales counts and straight lines for the redemption counts. Notably, the inverted redemption counts are plotted for better visualization alongside the sales data. This figure highlights consistent seasonal patterns, with both ticket sales and redemptions peaking during the summer months, from June to August, across most years. The dip observed in 2020 reflects the significant impact of the COVID-19 pandemic on ferry operations, with reduced ferry usage compared to previous years. These trends show the importance of flexible operational planning to accommodate both predictable seasonal demand and unexpected disruptions.

@@

  # Set symmetrical y-axis limits for both Sales and Redemption
  scale_y_continuous(limits = c(-max_count, max_count),
                     breaks = seq(-max_count, max_count, by = 100000),
                     sec.axis = sec_axis(~ -., name = "Sales Count (straight lines)")) +

@@

  # Apply minimal theme and customize axis titles
  theme_minimal() +
  theme(
    axis.title.y.right = element_text(color = "black", size = 12, margin = margin(r = 10)),
    axis.title.y.left = element_text(color = "black", size = 12, margin = margin(l = 10)),
    plot.title = element_text(hjust = 0.5, size = 16),
    legend.title = element_text(size = 12),
    legend.text = element_text(size = 10),
    axis.text.y = element_text(size = 10),
    axis.ticks.y = element_blank()
  )

>>>>

@fig-linePlot2 shows the Redemption and Sales Counts in months over years. The graph uses dashed lines to represent the monthly sales counts and straight lines for the redemption counts. Notably, the inverted redemption counts are plotted for better visualization alongside the sales data. This figure highlights consistent seasonal patterns, with both ticket sales and redemptions peaking during the summer months, from June to August, across most years. The dip observed in 2020 reflects the significant impact of the COVID-19 pandemic on ferry operations, with reduced ferry usage compared to previous years. These trends show the importance of flexible operational planning to accommodate both predictable seasonal demand and unexpected disruptions.

@@

  # Set symmetrical y-axis limits for both Sales and Redemption
  scale_y_continuous(
    limits = c(-max_count, max_count),
    breaks = seq(-max_count, max_count, by = 100000),
    labels = function(x) abs(x),  # Remove the negative signs from lower half labels
    sec.axis = sec_axis(~ -., name = "Sales Count (straight lines)")
  ) +

@@

  # Apply minimal theme and customize axis titles
  theme_minimal() +
  theme(
    axis.title.y.right = element_text(color = "black", size = 12, margin = margin(r = 10)),
    axis.title.y.left = element_text(color = "black", size = 12, margin = margin(l = 10)),
    axis.text.y.right = element_blank(),  # Hide axis values of the right y-axis
    plot.title = element_text(hjust = 0.5, size = 16),
    legend.title = element_text(size = 12),
    legend.text = element_text(size = 10),
    axis.text.y = element_text(size = 10),
    axis.ticks.y = element_blank()
  )
